Concurrent Programming in Harmony

### 2022-01-06 book/paper.tex
Latest

As an example of using modules,
\autoref{fig:hanoi} uses (or abuses?) Harmony to solve the
\emph{Towers of Hanoi} problem.
There are three towers with disks of varying sizes.
In the initial configuration, the first tower has three disks (of
sizes 1, 2, and 3), with the largest disk at the bottom, while the
other two towers are empty.  You are allowed to move a top disk
from one tower to another, but you are not allowed to stack a larger
disk on a smaller one.  The objective is to move the disks from the
first tower to the third one.

>>>>

As an example of using <{import}> and <{let}>,
\autoref{fig:hanoi} solves the \emph{Towers of Hanoi} problem.
If you are not familiar with this problem:
there are three towers with disks of varying sizes.
In the initial configuration, the first tower has three disks (of
sizes 1, 2, and 3), with the largest disk at the bottom, while the
other two towers are empty.  You are allowed to move a top disk
from one tower to another, but you are not allowed to stack a larger
disk on a smaller one.  The objective is to move the disks from the
first tower to the third one.
